exponential_BT

### 2025-04-02 inst/exponential_BT.Rmd
more work on exponential model

```{r ninetwelve, cache=TRUE}
n <- 12
a_try <- seq(from=0.01,to=0.99,len=10)
p_try <- ceiling(n * a_try)
x_try <- seq(from = 0.1, to = 1, by = 0.1)
jj <- as.matrix(expand.grid(p_try, x_try))
II <- t(apply(jj,1,function(v){getprob(n, v[1], v[2], N=1e4)}))
head(II)
tail(II)
S912 <- matrix(II[,11],length(a_try),length(x_try))
```

```{r show912}
S912 <- S912/max(S912)
contour(p_try,a_try,log(S912))
```

>>>>

```{r ninetwelve}
a_try <- seq(from=0.01,to=0.99,len=10)
x_try <- seq(from = 0.1, to = 1, by = 0.1)
single_like_fun <- function(n,a){
    p_try <- ceiling(n * a_try)
    jj <- as.matrix(expand.grid(p_try, x_try))
    II <- t(apply(jj,1,function(v){getprob(n, v[1], v[2], N=1e4)}))
    matrix(II[,ceiling(a*n)+2],length(a_try),length(x_try))
}
```

```{r makesupp912, cache=TRUE}
allsupp <- list(
    log(single_like_fun(12, a = 6/12)),
    log(single_like_fun(17, a = 7/17)),
    log(single_like_fun(23, a =12/23)),
    log(single_like_fun(09, a = 5/09)),
    log(single_like_fun(06, a = 7/13)),
    log(single_like_fun(08, a = 4/18)),
    log(single_like_fun(13, a = 8/13))
)
```

```{r show912}
S <- Reduce("+",allsupp)
contour(a_try, x_try, S-max(S))
```
